\subsection{}



\subsubsection{}

An object~$G$ of the category~$[\cat{B}, \cat{C}]$ is a functor from~$\cat{B}$ to~$\cat{C}$.
The functor~$J ∘ (\ph)$ assigns to it the composite functor~$J G$, which is an object of~$[\cat{B}, \cat{D}]$.
Any morphism~$α$ in~$[\cat{B}, \cat{C}]$ is of the form
\[
	α \colon G \to H \,,
\]
for some objects~$G$ and~$H$ of~$[\cat{B}, \cat{C}]$.
This then means that~$α$ is a natural transformation from~$G$ to~$H$.
The functor~$J ∘ (\ph)$ assigns to it the natural transformation~$J α$ from~$J G$ to~$J H$.

Suppose fist the functor~$J$ is faithful, and let~$α$ and~$β$ be two parallel morphisms in~$[\cat{B}, \cat{C}]$ that have the same image under~$J ∘ (\ph)$.
In other words,~$α$ and~$β$ are two natural transformations of the form
\[
	α, β \colon G \To H
\]
for two functors~$G$ and~$H$ from~$\cat{B}$ to~$\cat{C}$, and we have~$J α = J β$.
This means that for every object~$B$ of~$\cat{B}$, we have the equalities
\[
	J( α_B )
	=
	(J α)_B
	=
	(J β)_B
	=
	J( β_B ) \,.
\]
It follows that~$α_B = β_B$ for every object~$B$ of~$\cat{B}$ because the functor~$J$ is faithful, and therefore~$α = β$.
This shows that the induced functor~$J ∘ (\ph)$ is again faithful.

Suppose now that the functor~$J$ is fully faithful.
Let~$G$ and~$H$ be two objects of~$[\cat{B}, \cat{C}]$, i.e., functors from~$\cat{B}$ to~$\cat{C}$, and let~$β$ be a natural transformation from the resulting functor~$J G$ to the resulting functer~$J H$.
We claim that there exists a natural transformation~$α$ from~$G$ to~$H$ with~$β = J α$.
(This natural transformation is then unique since~$J$ is faithful, as seen above.)

For every object~$B$ of~$\cat{B}$, the component~$β_B$ is a morphism from~$J G(B)$ to~$J H(B)$.
There exists a unique morphism~$α_B$ from~$G(B)$ to~$H(B)$ with~$β_B = J(α_B)$ because the functor~$J$ is fully faithful.
These morphisms assemble into a transformation~$α$ from~$G$ to~$H$.
We need to show that this transformation~$α$ is natural.
We hence need to show that for every morhism
\[
	f \colon B \to B'
\]
in~$\cat{B}$ the following diagram commutes:
\[
	\begin{tikzcd}[sep = large]
		G(B)
		\arrow{r}[above]{G(f)}
		\arrow{d}[left]{α_B}
		&
		G(B')
		\arrow{d}[right]{α_{B'}}
		\\
		H(B)
		\arrow{r}[above]{H(f)}
		&
		H(B')
	\end{tikzcd}
\]
By applying the functor~$J$ to this diagram, we get the following diagram
\[
	\begin{tikzcd}[sep = large]
		J G(B)
		\arrow{r}[above]{J G(f)}
		\arrow{d}[left]{β_B}
		&
		J G(B')
		\arrow{d}[right]{β_{B'}}
		\\
		J H(B)
		\arrow{r}[above]{J H(f)}
		&
		J H(B')
	\end{tikzcd}
\]
We know that this second diagram commutes by the naturality of~$β$.
It follows that the first diagram also commutes because the functor~$J$ is faitful.
More explicitly, the commutativity of the second diagram tells us that
\begin{align*}
	J( α_{B'} ∘ G(f) )
	&=
	J( α_{B'} ) ∘ J G(f)
	\\
	&=
	β_{B'} ∘ J G(f)
	\\
	&=
	J H(f) ∘ β_B
	\\
	&=
	J H (f) ∘ J( α_B )
	\\
	&=
	J( H(f) ∘ α_B ) \,,
\end{align*}
from which it follows that
\[
	α_{B'} ∘ G(f) = H(f) ∘ α_B
\]
because~$J$ is faithful.

We have overall shows that the functor~$J$ is again fully faithful.

%\begin{remark}
%	The given assertian can also be proven in a less constructive way as follows.
%
%	We consider first the case that~$J$ is essentially surjective.
%	It is then an equivalence of categories from~$\cat{C}$ to~$\cat{D}$.
%	There hence exists a functor~$K$ from~$\cat{D}$ to~$\cat{C}$ with
%	\[
%		K J ≅ \Id_{\cat{C}} \,,
%		\quad
%		J K ≅ \Id_{\cat{D}} \,.
%	\]
%	It follows for the induced functors
%	\[
%		J_* \colon [\cat{B}, \cat{C}] \to [\cat{B}, \cat{D}] \,,
%		\quad
%		K_* \colon [\cat{B}, \cat{D}] \to [\cat{B}, \cat{C}]
%	\]
%	that again
%	\[
%		K_* ∘ J_*
%		=
%		(K ∘ (\ph)) ∘ (J ∘ (\ph))
%		=
%		(K J) ∘ (\ph)
%		≅
%		\Id_{\cat{C}} ∘ (\ph)
%		=
%		\Id_{[\cat{B}, \cat{C}]} \,,
%	\]
%	and similarly
%	\[
%		J_* ∘ K_* ≅ \Id_{[\cat{B}, \cat{D}]} \,.
%	\]
%	This shows that the functor~$J_*$ is again an equivalence of categories, and therefore in particular fully faithful.
%
%	We the general case, letet~$\cat{C}'$ be the essential image of~$J$.
%	In other words, let~$\cat{C}'$ be the full subcategory of~$\cat{D}$ consisting of all those objects~$D$ of~$\cat{D}$ for which there exists an object~$C$ of~$\cat{C}$ with~$D ≅ J(C)$.
%	The functor~$J$ factors as
%	\[
%		J = I ∘ J'
%	\]
%	where~$J'$ is the restriction of~$J$ to a functor from~$\cat{C}$ to~$\cat{C}'$, and~$I$ is the inclusion functor from~$\cat{C}'$ to~$\cat{C}$.
%
%	The functor~$J'$ is again fully faithful, and it is essentially surjective.
%	It is therefore an equivalence of categories.
%	We have seen above that the induces functor~$J' ∘ (\ph)$ is therefore again fully faithful.
%
%\end{remark}



\subsubsection{}

The induced functor~$J ∘ (\ph)$ from~$[\cat{B}, \cat{C}]$ to~$[\cat{B}, \cat{D}]$ is again fully faithful, whence the assertion follows from Lemma~4.3.8.



\subsubsection{}

We have the natural isomorphimsm
\[
	\cat{A}(\ph, G(\ph))
	≅
	\cat{B}(F(\ph), \ph)
	≅
	\cat{A}(\ph, G'(\ph))
\]
of functors from~$\cat{A}^{\op} × \cat{B}$ to~$\Set$.
Let
\[
	H \colon \cat{A}^{\op} \to [\cat{A}, \Set]
\]
denote the contravariant Yoneda embedding of~$\cat{A}$.
This functor~$H$ is fully faithful, and we might rephrase the natural isomorphism
\[
	\cat{A}(\ph, G(\ph)) ≅ \cat{A}(\ph, G'(\ph))
\]
as the isomorphism
\[
	H ∘ G ≅ H ∘ G' \,.
\]
It follows from part~(b) of this exercise that already~$G ≅ G'$ because~$H$ is fully faithful.
