\subsection{}



\subsubsection{}

There exists by assumption a functor~$G$ from~$\cat{B}$ to~$\cat{A}$ such that
\[
	G ∘ F ≅ \Id_{\cat{A}} \,,
	\quad
	F ∘ G ≅ \Id_{\cat{B}} \,.
\]
The isomorphism~$F ∘ G ≅ \Id_{\cat{B}}$ entails that
\[
	F(G(B)) ≅ B
\]
for every object~$B$ of~$\cat{B}$.
This shows that the functor~$F$ is essentially surjective.

To show that~$F$ is full and faithful let~$A$ and~$A'$ be two objects of~$\cat{A}$.
Let
\[
	α \colon G ∘ F \To \Id_{\cat{A}}
\]
be a natural isomorphism.
The square diagram
\[
	\begin{tikzcd}
		GF(A)
		\arrow{r}[above]{GF(f)}
		\arrow{d}[left]{α_A}
		&
		GF(A')
		\arrow{d}[right]{α_{A'}}
		\\
		A
		\arrow{r}[above]{f}
		&
		A'
	\end{tikzcd}
\]
commutes for every morphism~$f$ from~$A$ to~$A'$ in~$\cat{A}$.
We thus have
\[
	α_{A'} ∘ GF(f) ∘ α_A^{-1} = f
\]
for every such morphism~$f$.
In other words, the composite
\begin{equation}
	\label{composition_is_identity}
	\cat{A}(A, A')
	\xto{F}
	\cat{B}(F(A), F(A'))
	\xto{G}
	\cat{A}(GF(A), GF(A'))
	\xto{α_{A'} ∘ (\ph) ∘ α_A^{-1}}
	\cat{A}(A, A')
\end{equation}
is the identity map.
The first step of this composite, i.e., the map
\[
	\cat{A}(A, A')
	\xto{F}
	\cat{B}(F(A), F(A')) \,,
\]
therefore is injective.
This shows that the functor~$F$ is faithful.

Let us now show that the functor~$G$ is full.
We have seen that the composite~\eqref{composition_is_identity} is the identity map for any two objects~$A$ and~$A'$ of~$\cat{A}$.
The last step of this composite, i.e., the conjugation map~$α_{A'} ∘ (\ph) ∘ α_A^{-1}$, is bijective, whence we find that the map
\[
	\cat{B}(F(A), F(A'))
	\xto{G}
	\cat{A}(GF(A), GF(A'))
\]
is surjective.
This tells us that~$G$ is \enquote{full on the image on~$F$}.
But we need to show that the map
\[
	\cat{B}(B, B')
	\xto{G}
	\cat{A}(G(B), G(B'))
\]
is surjective for \emph{any} two objects~$B$ and~$B'$ of~$\cat{B}$.

Thankfully, we already know that the functor~$F$ is essentially surjective.
For the given two objects~$B$ and~$B'$ of~$\cat{B}$ there hence exist objects~$A$ and~$A'$ of~$\cat{A}$ for which there exists isomorphisms
\[
	g \colon F(A) \to B \,,
	\quad
	g' \colon F(A') \to B' \,.
\]
The square diagram
\[
	\begin{tikzcd}[column sep = 7em]
		\cat{B}(F(A), F(A'))
		\arrow{r}[above]{g' ∘ (\ph) ∘ g^{-1}}
		\arrow{d}[left]{G}
		&
		\cat{B}(B, B')
		\arrow{d}[right]{G}
		\\
		\cat{B}(GF(A), GF(A'))
		\arrow{r}[above]{G(g') ∘ (\ph) ∘ G(g)^{-1}}
		&
		\cat{B}(G(B), G(B'))
	\end{tikzcd}
\]
commutes by the functoriality of~$G$.
The two horizontal maps in this diagram are bijections because~$g$ and~$g'$ are isomorphisms.
We have seen above that the vertical map on the left-hand side is surjective.
It follows that the vertical map on the right-hand side is again surjective, which shows the desired surjectivity.

We have thus shown that the functor~$G$ is full.
By swapping the roles of~$F$ and~$G$, we find that~$F$ is full.

We have shown that equivalences are faithful, full, and essentially surjective.



\subsubsection{}

Let~$F$ be a functor from~$\cat{A}$ to~$\cat{B}$ that is faithful, full, and essentially surjective.
There exists for every object~$B$ of~$\cat{B}$ an object~$G(B)$ of~$\cat{A}$ for which there exists an isomorphism
\[
	ε_B \colon FG(B) \to B \,.
\]
For every morphism~$g \colon B \to B'$ in~$\cat{B}$, the conjugate
\[
	ε_{B'}^{-1} ∘ g ∘ ε_B
\]
is a morphism from~$FG(B)$ to~$FG(B'))$.
It follows that there exists a unique morphism~$G(g)$ from~$G(B)$ to~$G(B')$ such that
\[
	FG(g) = ε_{B'}^{-1} ∘ g ∘ ε_B
\]
because the functor~$F$ is both full (showing the existence of~$G(g)$) and faithful (showing the uniqueness of~$G(g)$).

The assignment~$G$ is a functor from~$\cat{B}$ to~$\cat{A}$:
\begin{itemize}

	\item
		For every object~$B$ of~$\cat{B}$, we have the equalities
		\[
			ε_B^{-1} ∘ \id_B ∘ ε_B
			=
			ε_B^{-1} ∘ ε_B
			=
			\id_{FG(B)}
			=
			F(\id_{G(B)}) \,.
		\]
		This shows that the morphism~$\id_{G(B)}$ satisfies the defining property of the morphism~$G(\id_B)$, so that
		\[
			G(\id_B) = \id_{G(B)} \,.
		\]

	\item
		For any two composable morphisms
		\[
			g \colon B \to B' \,,
			\quad
			g' \colon B' \to B''
		\]
		in~$\cat{B}$, we have the equalities
		\begin{align*}
			ε_{B''}^{-1} ∘ g' ∘ g ∘ ε_B
			&=
			ε_{B''}^{-1} ∘ g' ∘ ε_{B'} ∘ ε_{B'}^{-1} ∘ g ∘ ε_B
			\\
			&=
			F(G(g')) ∘ F(G(g))
			\\
			&=
			F(G(g') ∘ G(g)) \,.
		\end{align*}
		This shows that the composite~$G(g') ∘ G(g)$ satisfies the defining property of the morphism~$G(g' ∘ g)$, so that
		\[
			G(g' ∘ g) = G(g') ∘ G(g) \,.
		\]

\end{itemize}
This shows that the assignment~$G$ is indeed a functor.

The family~$ε = (ε_B)_{B ∈ \Ob(\cat{B})}$ is (by construction) a natural isomorphism from~$FG$ to~$\Id_{\cat{B}}$.
In the following, we will construct a natural isomorphism~$α$ from~$GF$ to~$\Id_{\cat{A}}$.

We have for every object~$A$ of~$\cat{A}$ the morphism
\[
	ε_{F(A)}
	\colon
	FGF(A) \to F(A)
\]
in~$\cat{B}$.
It follows that there exists a unique morphism
\[
	α_A
	\colon
	GF(A) \to A
\]
in~$\cat{A}$ such that~$ε_{F(A)} = F(α_A)$, because the functor~$F$ is both full (showing the existence of~$α_A$) and faithful (showing the uniqueness of~$α_A$).
The morphism~$α_A$ is an isomorphism because the functor~$F$ is full and faithful and therefore reflects isomorphisms by the following \lcnamecref{full and faithful reflects isomorphisms}.

\begin{lemma}
	\label{full and faithful reflects isomorphisms}
	Let~$\cat{A}$ and~$\cat{B}$ be two categories and let~$F$ be a functor from~$\cat{A}$ to~$\cat{B}$ that is both full and faithful.
	Let~$f$ be a morphism in~$\cat{A}$ such that~$F(f)$ is an isomorphism.
	Then~$f$ is an isomorphism.
\end{lemma}

\begin{proof}
	Let~$A$ be the domain of the morphism~$f$, and let~$A'$ be its codomain.
	We have in~$\cat{B}$ the morphism~$F(f)^{-1}$ from~$F(A')$ to~$F(A)$.
	There exists a morphism~$f'$ from~$A'$ to~$A$ with
	\[
		F(f') = F(f)^{-1}
	\]
	because the functor~$F$ is full.
	We find for the morphism~$f' ∘ f$ from~$A$ to~$A$ that
	\[
		F(f' ∘ f) = F(f') ∘ F(f) = F(f)^{-1} ∘ F(f) = \id_{F(A)} = F(\id_A) \,.
	\]
	It follows that~$f' ∘ f = \id_A$ because the functor~$F$ is faithful.
	We find in the same way that also~$f ∘ f' = \id_{A'}$.
	We have thus shown that the morphism~$f$ is an isomorphism with inverse given by~$f'$.
\end{proof}

The resulting family~$α = (α_A)_{A ∈ \Ob(\cat{A})}$ is a natural isomorphism from~$GF$ to~$A$.
We still need to prove the naturality of~$α$.
To this end we need to check that for every morphism
\[
	f \colon A \to A'
\]
in~$\cat{A}$, the following square diagram commutes:
\[
	\begin{tikzcd}
		GF(A)
		\arrow{r}[above]{GF(f)}
		\arrow{d}[left]{α_A}
		&
		GF(A')
		\arrow{d}[right]{α_{A'}}
		\\
		A
		\arrow{r}[above]{f}
		&
		A'
	\end{tikzcd}
\]
It suffices to show that this diagram commutes after we apply the functor~$F$ to it, because~$F$ is faithful.
We hence need to show that the following square diagram commutes:
\[
	\begin{tikzcd}[column sep = huge]
		FGF(A)
		\arrow{r}[above]{FGF(f)}
		\arrow{d}[left]{ε_{F(A)}}
		&
		FGF(A')
		\arrow{d}[right]{ε_{F(A')}}
		\\
		F(A)
		\arrow{r}[above]{F(f)}
		&
		F(A')
	\end{tikzcd}
\]
This desired commutativity follows from the naturality of~$ε$.

The existence of the natural isomorphisms
\[
	ε \colon FG \To \Id_{\cat{B}} \,,
	\quad
	α \colon GF \To \Id_{\cat{A}}
\]
shows that the two functors~$F$ and~$G$ form an equivalence between the categories~$\cat{A}$ and~$\cat{B}$.
This entails that~$F$ is an equivalence of categories.
