\subsection{}



\subsubsection{}

\begin{description}
	
	\item[Example~1.2.3,~(a)]
		The forgetful functor~$U$ from~$\Grp$ to~$\Set$ is faithful.
		But it is not full:
		Let~$G$ be the trivial group, let~$H$ be a non-trivial group and let~$h$ be a non-identity element of~$H$.
		The map~$U(G) \to U(H)$ given by~$1 \mapsto h$ is not a homomorphism of groups, and is therefore not contained in the image of~$U$.

	\item[Example~1.2.3,~(b)]
		The forgetful functor~$U$ from~$\Ring$ to~$\Set$ is faithful.
		But it is not full:
		Let both~$R$ and~$S$ be the ring of integers, i.e., the ring~$ℤ$.
		The map
		\[
			f
			\colon
			ℤ \to ℤ \,,
			\quad
			n \mapsto 2n
		\]
		is not a homomorphism of rings.
		It is therefore not contained in the image of~$U$.

	\item[Example~1.2.3,~(c)]
		The forgetful functor from~$\Ring$ to~$\Ab$ is faithful.
		But it is not full:
		this can be seen from the same counterexample as for the previous functor.

		The forgetful functor~$U$ from~$\Ring$ to~$\Mon$ is faithful.
		But it is not full:
		Let both~$R$ and~$S$ be the ring of integers, i.e., the ring~$ℤ$, and let~$f$ be the trivial homomorphism of monoids from~$U(R)$ to~$U(S)$.
		The map~$f$ is not a homomorphism of rings from~$R$ to~$S$, and therefore not contained in the image of~$U$.

	\item[Example~1.2.3,~(d)]
		The inclusion functor from~$\Ab$ to~$\Grp$ is both faithful and full since~$\Ab$ is a full subcategory of~$\Grp$.

	\item[Example~1.2.4,~(a)]
		The free functor~$F$ from~$\Set$ to~$\Grp$ is faithful:
		Let~$S$ and~$T$ be two sets and let~$f$ be a map from~$S$ to~$T$.
		The induced homomorphism of groups~$F(f)$ from~$F(S)$ to~$F(T)$ satisfies the condition
		\[
			F(f)(s)
			=
			f(s)
		\]
		for every element~$s$ of~$S$.
		The original map~$f$ is therefore uniquely determined by its induced homomorphism of groups~$F(f)$.

		But the functor~$F$ is not full:
		Let~$S$ be a non-empty set and let~$T$ be the empty set.
		There exists no map from~$S$ to~$T$, but there exist a homomorphism of groups from~$F(S)$ to~$F(T)$ (namely the trivial homomorphism).

	\item[Example~1.2.4,~(b)]
		The free functor from~$\Set$ to~$\CRing$ is faithful, but not full.
		This can be seen as in the previous example.

	\item[Example~1.2.4,~(c)]
		The free functor from~$\Set$ to~$\Vect{𝕜}$ is faithful, but not full.
		This can be seen as in the previous example.

	\item[Example~1.2.5,~(a)]
		The functor~$\fgroup_1$ from~$\Top_*$ to~$\Grp$ is not faithful.
		To see this, we consider the pointed topological space~$(ℝ, 0)$.
		The fundamental group~$\fgroup_1(ℝ, 0)$ is trivial, whence there exists precisely one homomorphism of groups from~$\fgroup_1(ℝ, 0)$ to~$\fgroup_1(ℝ, 0)$.
		But there exist many more continuous maps from~$(ℝ, 0)$ to~$(ℝ, 0)$.%
		\footnote{
			Namely,~$2^{ℵ_0}$ many.
		}

		The functor~$\fgroup_1$ is also not full.
		The author doesn’t know a good example for this, and refers to \cite{stackexchange_pi_1_not_full}.

	\item[Example~1.2.5,~(b)]
		The author strongly suspects that these functors are neither faithful nor full, but isn’t good enough at topology to give examples that confirm these suspicions.

	\item[Example~1.2.7]
		The functor~$F$ from~$\cat{G}$ to~$\cat{H}$ is faithful if and only if the corresponding homomorphism of groups~$f$ from~$G$ to~$H$ is injective.
		Similarly, the functor~$F$ is full if and only if the corresponding homomorphism~$f$ is surjective.

	\item[Example~1.2.8]
		This functor is faithful if and only if the corresponding~\set{$G$}, respectively representation of~$G$, is faithful.

	\item[Example~1.2.9]
		This functor is faithful, because there exists for any two elements~$a$ and~$a'$ of~$A$ at most one morphism from~$a$ to~$a'$ in~$\cat{A}$.
		It is full if and only if it follows for any two elements~$a$ and~$a'$ of~$\cat{A}$ from~$f(a) ≤ f(a')$ that also~$a ≤ a'$.

	\item[Example~1.2.11]
		The given functor~$C$ from~$\Top$ to~$\Ring$ is not faithful.
		To see this, let~$X ≔ \{ x \}$ be the one-point topological space and let~$Y ≔ \{ y_1, y_2 \}$ be the two-point indiscrete topology space.
		Both~$C(X)$ and~$C(Y)$ consist only of constant functions, and the two continuous maps from~$X$ to~$Y$ induce the same homomorphism of rings from~$C(Y)$ to~$C(X)$.

		The functor~$C$ is also not full.
		The author doesn’t have a (counter)example for this, and refers to \cite{stackexchange_continuous_functions_functor_not_full}.

	\item[Example~1.2.12]
		The functor~$(\ph)^*$ from~$\Vect{\kf}$ to~$\Vect{\kf}$ is faithful.
		To see this, let~$V$ and~$W$ be two~\vectorspaces{$𝕜$} and let~$f_1$ and~$f_2$ be two distinct linear maps from~$V$ to~$W$.
		There exists by assumption a vector~$v$ in~$V$ for which the two vectors~$w_1 ≔ f_1(v)$ and~$w_2 ≔ f_2(v)$ in~$W$ are distinct.
		It follows that there exists some linear functional~$w^*$ in~$W^*$ with~$w^*(w_1) ≠ w^*(w_2)$.
		It further follows that
		\begin{align*}
			\SwapAboveDisplaySkip
			f_1^*(w^*)(v)
			&=
			(w^* ∘ f_1)(v)
			\\
			&=
			w^*( f_1(w) )
			\\
			&=
			w^*(w_1)
			\\
			&≠
			w^*(w_2)
			\\
			&=
			\dotsb
			\\
			&=
			f_2^*(w^*)(v) \,.
		\end{align*}
		This shows that~$f_1^*(w^*) ≠ f_2^*(w^*)$, and therefore~$f_1^* ≠ f_2^*$.

		However, the functor~$(\ph)^*$ is not full.
		To see this, we observe that for any two~\vectorspaces{$𝕜$}~$V$ and~$W$, the map
		\[
			D_{V, W}
			\colon
			\Hom_{𝕜}(V, W) \to \Hom_{𝕜}(W^*, V^*) \,,
			\quad
			f \mapsto f^*
		\]
		is linear.
		For~$V = 𝕜$, the domain of~$D_{V, W}$ is given by
		\[
			\Hom_{𝕜}(V, W) = \Hom_{𝕜}(𝕜, W) ≅ W \,,
		\]
		while its codomain is given by
		\[
			\Hom_{𝕜}(W^*, V^*)
			=
			\Hom_{𝕜}(W^*, 𝕜^*)
			≅
			\Hom_{𝕜}(W^*, 𝕜)
			=
			W^{**} \,.
		\]
		If we choose the vector space~$W$ to be infinite-dimensional, then it follows that the map~$D_{𝕜, W}$ cannot be surjective, since~$W^{**}$ is of strictly larger dimension than~$W$.

\end{description}



\subsubsection{}

Let~$\Two$ be the category given by two objects~$0$ and~$1$ and one non-identity morphism~$i$, going from~$0$ to~$1$.
This category may be depicted as follows:
\[
	\Two
	\colon
	\begin{tikzcd}
		0
		\arrow{r}[above]{i}
		&
		1
	\end{tikzcd}
\]
Let similarly~$\Two'$ be the category given by two objects~$0$ and~$1$ and two parallel non-identity morphisms from~$0$ to~$1$, denoted by~$i$ and~$i'$.
This category may be depicted as follows:
\[
	\Two'
	\colon
	\begin{tikzcd}
		0
		\arrow[yshift= 0.5ex]{r}[above]{i}
		\arrow[yshift=-0.5ex]{r}[below]{i'}
		&
		1
	\end{tikzcd}
\]
The inclusion functor
\[
	I
	\colon
	\Two \to \Two'
	\quad\text{with}\quad
	F(0) = 0 \,,
	\quad
	F(1) = 1 \,,
	\quad
	F(i) = i
\]
is faithful but not full.
The retraction functor
\[
	R
	\colon
	\Two' \to \Two
	\quad\text{with}\quad
	F(0)  = 0 \,,
	\quad
	F(1)  = 1 \,,
	\quad
	F(i)  = i
	\quad
	F(i') = i
\]
is full but not faithful.
The composite~$R ∘ I$ is the identity functor on~$\Two$, which is both full and faithful.
The composite~$I ∘ R$ is neither full nor faithful.
