\subsection{}



\subsubsection{}

We can use the strategy developed in Exercise~2.3.14 to see that the category~$\Mon$ is not essentially small.
It is therefore also not small.
It is, however, locally small, since it admits a faithful functor to the locally small category~$\Set$.



\subsubsection{}

The given category is small because its collection of morphisms is the underlying set of~$ℤ$.
This entails that the given category is both essentially small and locally small.



\subsubsection{}

The given category is locally small because there exists at most one morphism between any two objects of its objects.
Its class of objects is the underlying set of~$ℤ$, and therefore a set.
It follows that this category is small, and therefore also essentially small.



\subsubsection{}

We can regard every set as a discrete category.
This allows us to regard~$\Set$ as a full subcategory of~$\Cat$.
Two sets are isomorphic if and only if they are isomorphic as discrete categories.
The inclusion from~$\Set$ and~$\Cat$ does therefore induce an injection
\[
	\Set / {≅} \to \Cat / {≅} \,.
\]
It follows that if~$\Cat$ were to be essentially small, then~$\Set$ would also be essentially small.
But we know from Exercise~3.2.14 that this is not the case.

We therefore find that~$\Cat$ is not essentially small, and hence also not small.

The category~$\Cat$ is, however, locally small.
To see this, let~$\cat{A}$ and~$\cat{B}$ be two objects of~$\Cat$.
This means that both~$\cat{A}$ and~$\cat{B}$ are small categories.
Every functor from~$\cat{A}$ to~$\cat{B}$ is uniquely determined by its action on the morphisms of~$\cat{A}$, whence the class~$\Cat(\cat{A}, \cat{B})$ can be identified with a subset of the set~$\Mor(\cat{B})^{\Mor(\cat{A})}$.%
\footnote{
	We denote here for every category~$\cat{B}$ the class of morphisms in~$\cat{C}$ by~$\Mor(\cat{C})$.
}
This entails that~$\Cat(\cat{A}, \cat{B})$ is again a set.



\subsubsection{}

There exists for every family of cardinals~$(κ_i)_{i ∈ I}$ a cardinal~$λ$ that is distinct to each~$κ_i$.
(One may take for~$λ$ the cardinal associated to the power set of the sum~$∑_{i ∈ I} κ_i$.
This cardinal is then of strictly larger cardinality than each~$κ_i$.)
The collection of all cardinals is therefore a proper class, and not a set.
It follows that the given category is not locally small.
It is therefore not essentially small, and hence also not small.
