\subsection{}



\subsubsection{}

Let~$α$ be an isomorphism from~$X + Y$ to~$\HY_A$.
Let
\[
	i \colon X \To X + Y \,,
	\quad
	j \colon Y \To X + Y
\]
be natural transformations that realize~$X + Y$ as a coproduct of~$X$ and~$Y$, and let
\[
	β ≔ α ∘ i \colon X \To \HY_A \,,
	\quad
	γ ≔ α ∘ j \colon Y \To \HY_A \,.
\]

We know that colimits in~$[\cat{A}^{\op}, \Set]$ are computed pointwise.
This tells us that for every object~$A'$ of~$\cat{A}$, the two maps
\[
	i_{A'} \colon X(A') \to (X + Y)(A') \,,
	\quad
	j_{A'} \colon Y(A') \to (X + Y)(A')
\]
make the set~$(X + Y)(A')$ into a coproduct of the two sets~$X(A')$ and~$Y(A')$.
We know that the coproduct of two sets is given by their disjoint union.
The set~$(X + Y)(A')$ is therefore the disjoint union of the images of~$i_{A'}$ and~$j_{A'}$ (and both~$i_{A'}$  and~$j_{A'}$ are injective).
The map~$α_{A'}$ is a bijection from~$(X + Y)(A')$ to~$\HY_A(A')$, so it further follows that the set~$\HY_A(A')$ is the disjoint union of the images of~$α_{A'} ∘ i_{A'} = β_{A'}$ and~$α_{A'} ∘ j_{A'} = γ_{A'}$.

This entails that the set~$\cat{A}(A, A) = \HY_A(A)$ is the disjoint union of the images of~$β_{A'}$ and~$γ_{A'}$.
The element~$\id_A$ of~$\cat{A}(A, A)$ is therefore contained in precisely on of these two images.
We may assume that it is contained in the image of~$β_A$.

We check in the following that the set~$Y(A')$ is empty for every object~$A'$ of~$\cat{A}$.
We do so by showing the image of~$Y(A')$ in~$\HY_A(A')$ under~$γ_{A'}$ is empty.

Let~$x$ be a preimage of~$\id_A$ in~$X(A)$ under~$β_A$.
(This preimage is in fact unique, since~$β_A = α_A ∘ i_A$ is a composite of two injective maps.)
Let~$A'$ be an arbitrary object of~$\cat{A}$ and let~$f$ be an element of~$\HY_A(A')$.
This means that~$f$ is a morphism from~$A'$ to~$A$.
Then
\[
	f
	=
	\id_A ∘ f
	=
	f^*( \id_A )
	=
	\HY_A(f)( \id_A )
	=
	\HY_A(f)( β_A(x) )
	=
	β_{A'}( X(f)(x) )
\]
by the naturality of~$β$.
This shows that all of~$\HY_A(A')$ is contained in the image of~$β_{A'}$.
But~$\HY_A(A')$ is the disjoint union of the images of~$β_{A'}$ and~$γ_{A'}$.
We thus find that the image of~$γ_{A'}$ is empty, and therefore that~$Y(A')$ is empty.



\subsubsection{}

Let~$X$ and~$Y$ be two representable presheaves on~$\cat{A}$.
This means that there exists objects~$A$ and~$A'$ of~$\cat{A}$ with
\[
	X ≅ \HY_A \,,
	\quad
	Y ≅ \HY_{A'} \,.
\]
This entails that the sets
\[
	X(A) ≅ \HY_A(A) = \cat{A}(A, A) \,,
	\quad
	Y(A') ≅ \HY_{A'}(A') = \cat{A}(A', A')
\]
are non-empty because they contain the elements~$\id_A$ and~$\id_{A'}$ respectively.
It follows from part~(a) that the functor~$X + Y$ cannot be representable.
